Tools for identifying unexpectedly low microfossil count sums

### 2020-06-11 Rmd/count_check_MS.Rmd
Lake A (x3) moved and expanded

Dataset pollen1, published includes `r pollenA$n_samp` assemblages with a median richness of `r pollenA$taxa_median` taxa.
Count sums vary between `r pollenA$count_min` and `r pollenA$count_max`.
The greatest common divisor is three for all assemblages, that is all `r pollenA$n_count` counts in the dataset are divisible by three.

>>>>

Dataset pollen1, published includes `r pollenA$n_samp` assemblages with a median richness of `r pollenA$taxa_median` taxa.
Count sums vary between `r pollenA$count_min` and `r pollenA$count_max`.
The greatest common divisor is three for all assemblages: all `r pollenA$n_count` counts in the dataset are divisible by three. 
Assuming (optimistically) the distribution of counts is (at least locally) uniform, the probability of _n_ counts being divisible by _k_ is $1/k^n$.
For a dataset this large, the probability of having all counts divisible by three by chance is 10^`r ceiling(- pollenA$n_count * log10(3))`^.
Given this very small probability, it seems reasonable to conclude that the archived data are not the original counts, but I have no idea how they were generated.
